Education Serves as a Deterrent to Criminal Behaviour

### 2024-03-30 paper/paper.qmd
Update paper with table of contents

---
title: "Education Serves as a Deterrent to Criminal Behaviour"
author: Rahma Binth Mohammad
thanks: "Code and data are available at: <https://github.com/rahmabinth/education>"
date: 16 February 2024
date-format: long
abstract: "This paper explores the impact of Compulsory School Leaving (CSL) reforms on criminal behaviour, focusing on their role in reducing crime rates, particularly among the youth demographic. Drawing upon empirical evidence, it investigates how CSL reforms incentivize educational attainment, thereby diminishing the allure of criminal activities. The study underscores the significance of education in deterring individuals from a life of crime and advocates for continued research to inform effective policy interventions."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

- Federal Bureau of Investigation Uniform Crime Data [@fbi_ucr]
- Westlaw International Database [@westlaw]

@@

In general, these data sets provide us with a way to graph the arrest rates against the age for various crime type, compare the change in dropout ages as time passes, and see arrest rates prior and post to the reforms. We have omitted an in-depth examination of the discontinuity estimates for conciseness.

@@

# References

>>>>

---
title: "Education Serves as a Deterrent to Criminal Behaviour"
author: Rahma Binth Mohammad
thanks: "Code and data are available at: <https://github.com/rahmabinth/education>"
date: 16 February 2024
date-format: long
abstract: "This paper explores the impact of Compulsory School Leaving (CSL) reforms on criminal behaviour, focusing on their role in reducing crime rates, particularly among the youth demographic. Drawing upon empirical evidence, it investigates how CSL reforms incentivize educational attainment, thereby diminishing the allure of criminal activities. The study underscores the significance of education in deterring individuals from a life of crime and advocates for continued research to inform effective policy interventions."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

- Federal Bureau of Investigation Uniform Crime Data
- Westlaw International Database

@@

In general, these datasets provide us with a way to graph the arrest rates against the age for various crime type, compare the change in dropout ages as time passes, and see arrest rates prior and post to the reforms. We have omitted an in-depth examination of the discontinuity estimates for conciseness. Our analysis with this data provide us with information of the real world to help policy makers make decisions on future educational interventions.

@@

# References {#sec-refereces}
